\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{csquotes}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
    \item\small{
        \textbf{#1}{: #2 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{\href{https://www.linkedin.com/in/npchien/}{\Large Ngo Phu Chien}} & Email : \href{mailto:ngophuchien@outlook.com}{ngophuchien@outlook.com}\\
        \href{https://www.linkedin.com/in/npchien}{https://www.linkedin.com/in/npchien/} & Mobile : 0973668150 \\
    \end{tabular*}


%-----------EDUCATION-----------------
    \section{Education}
    \resumeSubHeadingListStart
    \resumeSubheading
    {University of Science - VNUHCM}{Ho Chi Minh City, Vietnam}
    {Bachelor of Science in Software Engineering;  GPA: 3.43 (8.54/10)}{Aug. 2019 -- Sep. 2023}
    \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
    \section{Experience}
    \resumeSubHeadingListStart

    \resumeSubheading
    {VNG Corporation - Zalo}{Ho Chi Minh City, Vietnam}
    {Senior Software Engineer}{Mar 2025 - Present}
    \resumeItemListStart
    \resumeItem{System Monitoring \& Observability}
    {Enhanced service monitoring to accurately measure and report system SLA, SLI, and SLO for backend storage services.}
    \resumeItem{Infrastructure Migration}
    {Improved system scalability and eliminated queue overflow issues by migrating from in-house queue solution to Kafka infrastructure. Due to lack of scheduling capabilities in Kafka, designed and implemented distributed event reminder service using Apache Ignite to handle delayed event processing and resend events to Kafka.}
    \resumeItem{Code Quality \& Architecture}
    {Refactored existing codebase to improve testability and maintainability by applying modern technologies such as dependency injection, enhancing system modularity and development efficiency.}
    \resumeItemListEnd

    \resumeSubheading
    {MoMo}{Ho Chi Minh City, Vietnam}
    {Software Engineer}{Jun 2022 - Mar 2025}
    \resumeItemListStart
    \resumeItem{Performance Optimization}
    {Achieved 95\% performance improvement (4s → 200ms) on promotion platform by developing streaming mechanism to overcome Firestore index limitations and return data immediately when sufficient results are available, reducing Firestore fees by 80\%.}
    \resumeItem{System Scalability}
    {Scaled mission platform to handle 20k RPS for status API with only 4 1-core pods and processed 6k+ user events/second in production with sub-200ms processing through complete re-architecture and refactoring, reducing user complaints by 50\%. Optimized caching performance by rewriting Lua scripts executed in Redis to reduce network round trips.}
    \resumeItem{Technology Migration \& Load Handling}
    {Enhanced system performance by migrating user ranking system from Bigtable to HBase, applying modern technique: asynchronous parameterized logging, optimized thread pools, caching, rate limiting, and retry backoff mechanisms. Optimized gift verification system for high-traffic Lac Xi campaigns by reducing redundant steps that could affect system stability.}
    \resumeItem{Security \& Distributed Systems}
    {Built secure authentication gateway with Keycloak integration and custom rule-based authorization engine. Designed clustered in-memory user segmentation system using Apache Ignite with PostgreSQL and consistent hashing. Implemented user-to-instance routing gateway with consistent hashing technique to reduce huge data movement and improve cache hit rates during large-scale campaigns.}
    \resumeItem{System Reliability \& Developer Experience}
    {Improved promotion \& gamification system reliability by refactoring core idempotency library, eliminating duplicate gift dispatching. Streamlined configuration tools with error-detection capabilities, reducing complexity and human errors for internal teams.}
    \resumeItem{Platform Maintenance}
    {Maintained and enhanced donation platform (Heo Dat MoMo) while resolving technical debt and developing new user engagement features with virtual rewards system.}
    \resumeItem{Framework Development}
    {Built Spring-like annotation framework leveraging existing Vert.x and Dagger 2 common libraries to reduce redundant code when initializing new services, improving development efficiency and code maintainability within the team.}
    \resumeItemListEnd

    \resumeSubheading
    {MoMo}{Ho Chi Minh City, Vietnam}
    {ITC Trainee - MoMo Talent Program}{Nov 2021 - Jun 2022}
    \resumeItemListStart
    \resumeItem{Lac Xi 2022}
    {Built high-availability microservices from scratch with seamless cross-service integration using GCP infrastructure (BigTable, BigQuery, Cloud Firestore, Cloud Pubsub).}
    \resumeItemListEnd

    \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
    \section{Projects}
    \resumeSubHeadingListStart
    \resumeSubItem{Drive Reader}{C\#/.NET. Reads FAT32/NTFS file systems using Windows low-level APIs, reconstructs the full directory tree of a given disk. \href{https://github.com/phuchienngo/DriveReader}{GitHub}}
    \resumeSubItem{SimpleKV}{Java/Kotlin. High-performance in-memory key-value database with I/O multiplexing, consistent hashing, LMAX Disruptor, buddy allocation for zero GC, and scalable DashTable. \href{https://github.com/phuchienngo/simplekv}{GitHub}}
    \resumeSubItem{TinyDB}{Java/Kotlin. Lightweight LSM-tree key-value embedded database with WAL, SSTables, MemTable, compaction, and bloom filters. Thread-safe and optimized for data integrity. \href{https://github.com/phuchienngo/tinydb}{GitHub}}
    \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
    \section{Programming Skills}
    \resumeSubHeadingListStart
    \resumeSubItem{Languages}
    {Java, Kotlin, Go, Python, JavaScript, SQL}
    \resumeSubItem{Technologies}
    {Vert.x, gRPC, Thrift, Bigtable, HBase, BigQuery, Postgres, Firestore, MongoDB, Cloud Pubsub, Kafka, Redis, DragonflyDB, Doris, Starrocks, Prometheus, Grafana, Docker, VictoriaMetrics}
    \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
